---
title: "Max"
author: "Max Tan 300526544"
date: '2022-08-20'
output: html_document
---

+---
title: "Exploratory Data Analysis"
author: "Lissa Harrop, Katrina Watkins, Ricky Loo and Max Tan"
date: "16 August 2022"
classoption: 12pt
  
header-includes:
  - \usepackage{newpxtext,eulerpx}
  - \usepackage{bm,bbm}
  - \usepackage{float}

output: bookdown::pdf_document2

#link-citations: yes
#bibliography: references.bib
#citation_package: biblatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(300526544, kind="Mersenne-Twister") #Mixture of all our ID numbers
require(ggplot2)
require(ggthemes)
require(extrafont)
require(booktabs)
require(GGally)
require(ggExtra)
require(xtable)
require(moments)
require(ggcorrplot)
require(fitdistrplus)
require(reshape2)
```

```{r, echo=FALSE}
lovoo <- read.csv("lovoo_v3_users_api-results.csv")
lovoo <- data.frame(lovoo)
lovoo <- lovoo[, c("age", "counts_pictures", "counts_profileVisits", "counts_kisses", "distance", "country", "isVip")]
lovoo$country <- as.factor(lovoo$country)
lovoo$isVip <- as.factor(lovoo$isVip)
head(lovoo)
dim(lovoo)
summary(lovoo)
```

```{r}
colSums(is.na(lovoo))
```
The only variable with missing values is distance.
```{r}
lovoo <- lovoo[, c("counts_profileVisits", "counts_kisses", "isVip")]
```
The variables that I will be looking at are "isVip" (whether or not the profile has purchased a paid membership), "counts_profileVisits" (how many visits their profile has accumulated) and "counts_kisses" (how many likes/matches their profile has accumulated).

How does profile visits affect profile likes?
```{r}
cormat <- round(cor(lovoo[, c("counts_profileVisits", "counts_kisses")]),2)
head(cormat)
melted_cormat <- melt(cormat)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```
We see that there is a high correlation (0.89) between profile visits and profile likes.
```{r}
plot(lovoo$counts_profileVisits, lovoo$counts_kisses, main="How do profile visits affect profile likes?",
   xlab="Profile Visits", ylab="Profile Likes")
abline(lm(lovoo$counts_kisses ~ lovoo$counts_profileVisits, data = lovoo), col = "red")
```
We see from the scatterplot that there is a positive relationship between profile visits and profile likes. We can also see there are several outliers that we should remove as they can be very influential to our data.
```{r}
Q1visits <- quantile(lovoo$counts_profileVisits, .25)
Q3visits <- quantile(lovoo$counts_profileVisits, .75)

Q1likes <- quantile(lovoo$counts_kisses, .25)
Q3likes <- quantile(lovoo$counts_kisses, .75)

IQRvisits <- IQR(lovoo$counts_profileVisits)
IQRlikes <- IQR(lovoo$counts_kisses)

lovoo <- subset(lovoo, lovoo$counts_profileVisits > (Q1visits - 1.5*IQRvisits) & lovoo$counts_profileVisits < (Q3visits + 1.5*IQRvisits))
lovoo <- subset(lovoo, lovoo$counts_kisses > (Q1likes - 1.5*IQRlikes) & lovoo$counts_kisses < (Q3likes + 1.5*IQRlikes))
```
Let's try the scatterplot again.
```{r}
plot(lovoo$counts_profileVisits, lovoo$counts_kisses, main="How do profile visits affect profile likes?",
   xlab="Profile Visits", ylab="Profile Likes")
abline(lm(lovoo$counts_kisses ~ lovoo$counts_profileVisits, data = lovoo), col = "red", lwd=2)
```
We see the same positive relationship but the outlieing profiles are gone.
```{r}
par(mfrow=c(1,2))
hist(lovoo$counts_profileVisits, main="Distribution of profile visits", xlab="Profile Visits")
hist(lovoo$counts_kisses, main="Distribution of profile likes", xlab="Profile Likes")
```
Does having "VIP" mean you get more profile visits and likes?

The distribution of profile visits and profile likes is right skewed and definetly does not follow a normal distribution.
```{r}
par(mfrow=c(1,2))
ggplot(lovoo, aes(x=counts_profileVisits, color=isVip)) + 
  geom_density() + labs(x="Profile Visits") + labs(color="VIP") + scale_color_discrete(labels=c('Yes', 'No'))
ggplot(lovoo, aes(x=counts_kisses, color=isVip)) + 
  geom_density() + labs(x="Profile Likes") + labs(color="VIP") + scale_color_discrete(labels=c('Yes', 'No')) + geom_vline(data=lovoo, aes(xintercept=mean(counts_kisses), color=isVip),
             linetype="dashed")
```
The density graphs for both profile visits and profile likes is right skewed. This means that for both profile likes and visits, the mean is greater than the median.
```{r}
par(mfrow=c(1,2))
boxplot(lovoo$isVip, lovoo$counts_profileVisits, names=c("Yes", "No"), main="Profie Visits by profiles with 'VIP'", ylab="Profile Visits")
boxplot(lovoo$isVip, lovoo$counts_kisses, names=c("Yes", "No"), main="Profie Likes by profiles with 'VIP'", ylab="Profile Likes")
```
The mean of the boxplot for profiles with "VIP" is less than the mean of the boxplot for profiles without "VIP", this means on average profiles with "VIP" get less profiles and likes than profiles without "VIP".