---
output:
  pdf_document: default
  html_document: default
---
+---
title: "Exploratory Data Analysis"
author: "Lissa Harrop, Katrina Watkins, Ricky Loo and Max Tan"
date: "16 August 2022"
classoption: 12pt
  
header-includes:
  - \usepackage{newpxtext,eulerpx}
  - \usepackage{bm,bbm}
  - \usepackage{float}

output: bookdown::pdf_document2

#link-citations: yes
#bibliography: references.bib
#citation_package: biblatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(300521444, kind="Mersenne-Twister") #Mixture of all our ID numbers
require(ggplot2)
require(ggthemes)
require(extrafont)
require(booktabs)
require(GGally)
require(ggExtra)
require(xtable)
require(moments)
require(ggcorrplot)
require(fitdistrplus)
require(reshape2)
require(farff)
```

```{r, echo=FALSE}
#lovoo <- read.csv("C:/Users/L Harrop/OneDrive/Study/STAT_394/Project/Group-Project/Data/CSV/lovoo_v3_users_api-results.csv")
# Need to set a relative path!
lovoo <- read.csv("../../Data/CSV/lovoo_v3_users_api-results.csv")
lovoo <- data.frame(lovoo)
lovoo <- lovoo[, c("age", "counts_pictures", "counts_profileVisits", "counts_kisses", "distance", "country", "isVip")]
lovoo
```

```{r}
lovoo$country <- as.factor(lovoo$country)
lovoo$isVip <- as.factor(lovoo$isVip)
summary(lovoo)
```

## Analysis of the factors: country, vip, & distance
### Creating a dataset of the assigned variables
```{r}
new_dataset <- lovoo[, c("distance", "country", "isVip")]
```

### Univariate Analysis

### Country
```{r}
barplot(table(new_dataset$country), col = "purple", las = 2, cex.names = 0.75, cex.axis = 0.75, main = "Country", xlab = "Country", ylab = "Count", ylim = c(1, 2000))
table(new_dataset$country)
```
It can be observed that the greatest number of users come from: CH, DE, FR, and IT. 

### Vip
```{r}
barplot(table(new_dataset$isVip), col = "purple", main = "Purchased Vip", xlab = "Purchased", ylab = "Count", ylim = c(1, 4000))
table(new_dataset$isVip)
```

The majority of users haven't purchased VIP. 

### Distance
```{r}
hist(new_dataset$distance, xlab = "Distance", ylab = "Count of Individuals", main = "Histogram of individuals preference of logged distance", col = "red")
table(new_dataset$distance)
```

### Logging the skewed data
```{r}
new_dataset$distance <- log(new_dataset$distance)
hist(new_dataset$distance, xlab = "Distance", ylab = "Count of Individuals", main = "Histogram of Individuals preference of logged distance", col = "green")
```

It can be observed that the data is left skewed. The majority of users, set distances higher than the median. 

# Bivariate


### Correlation between distance and isVip
```{r}
ggplot(new_dataset) +
  geom_boxplot(aes(x = distance, y = isVip)) + coord_flip()
```

### Correlation between country and distance
ggplot(new_dataset) +
  geom_bar(aes(x = country, fill = isVip))

table(new_dataset$country, new_dataset$isVip)

# Bivariate Analysis

# Correlation between country and VIP
```{r}
ggplot(new_dataset) +
  geom_bar(aes(x = country, fill = isVip))
```

It can be observed from this graph that CH, DE, FR and IT have the greatest number of users who have purchased VIP status.

